Accelerating Biomolecular Nuclear Magnetic Resonance Assignment with A*

### 2014-03-27 paper/tex/Paper.tex
paper update

\section{Assignment Methods} % (fold)
\label{sec:method}

\subsection{Manual Assignment} % (fold)
\label{sub:manual_assignment}
% TODO
add this part
cite our sources

@@

\subsection{Future Goals} % (fold)
\label{sub:future_goals}
In future research, we will look into maximizing speed and efficiency to the point that our algorithm can assign full amino acid sequences. In order to achieve this, we will experiment with  both parallelization (techniques) and machine learning. The latter of these two will assist in optimizing the cost calculation while the former will increase the speed of assignment. We believe these implementations will help our algorithm handle datasets with numerous missing data points, validating our results even when given incomplete data. 
% subsection future_goals (end)

% subsection algorithm (end)
% section method (end)
\bibliographystyle{amc}
\bibliography{Paper}

>>>>

\section{Assignment} % (fold)
\label{sec:method}

\subsection{Data Collection} % (fold)
\label{sub:data_collection}
Determining the structure of a protein requires many highly involved steps. The first, which can take at least five days, is protein production. NMR experiments are then performed using the produced proteins in order to gather the data necessary for the assignment process. This process usually takes another one to two days for every spectrum involved. The most time consuming process is assignment of the structure. \cite{babak_alipanahi_error_2011}

\subsection{Manual Assignment} % (fold)
\label{sub:manual_assignment}
% TODO
In most cases, backbone NMR data is assigned manually. However, with hundreds of values for the chemical shift values of C(a) and C(b), this process can take anywhere from 20 days to 9 months with perfect data. To complicate matters even more, experience has shown most data sets to have missing or false peaks, requiring whomever is doing the actual assignment to either skip large portions of the protein sequence or to guess where a certain chain is located in the sequence, making this method extremely error prone. \cite{babak_alipanahi_error_2011}

@@

\subsection{Future Goals} % (fold)
\label{sub:future_goals}
In future research, we will look into maximizing speed and efficiency to the point that our algorithm can assign full amino acid sequences. In order to achieve this, we will experiment with  both parallelization (techniques) and machine learning. The latter of these two will assist in optimizing the cost calculation while the former will increase the speed of assignment. We believe these implementations will help our algorithm handle datasets with numerous missing data points, validating our results even when given incomplete data. 
% subsection future_goals (end)
\nocite{guntert_automated_2009}
\nocite{brief_introduction_Poulsen}
% section method (end)
\bibliographystyle{amc}
\bibliography{Paper}
